Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-29 vertical-thermal-review.Rmd
add acknowledgements
@NidhiVinod , FYI. I added the people who have contributed figure materials and lab members for feedback (I especially mentioned Eleinis because she put a lot into her review). Please add others as you feel appropriate.

## Acknowledgements
Thanks to ...., the ForestGEO Ecosystems & Climate lab at SCBI for helpful discussion.
Funding was provided by the Smithsonian Institution, ....

>>>>

## Acknowledgements
Thanks to Norbert Kunert, Camille Piponiot, and Andrew Davies for providing figure materials. 
This manuscript benefited from feedback from Eleinis Ávila-Lovera, ... and the ForestGEO Ecosystems & Climate lab at SCBI.
Funding was provided by the Smithsonian Institution, ....
